---
title: "CEA_Spatial_analysis"
Name: Yuhan
Date: 11/15/2020
output: html_notebook
---
Seurat Version: 2.3.4


###Call for packages
```{r}
library(Seurat)
library(ggplot2)
library(tidyverse)
library(cowplot)
#library(clustree)
library(scclusteval)
packageVersion("Seurat")
```

###Load CEA mFISH data files

```{r}
m264A.mFISH=read.table("/Volumes/multifish/CEA_analysis/CEA_455264_A/analysis/1_raw_v2/count_roi_v2.csv",sep=",",as.is=T,row.names=1,header= TRUE)

m264A.mFISH=t(m264A.mFISH)

row=c("Oprk1_R12", "Vipr2_R12", "Scn4b_R12", "Scn4b_R13")
m264A.mFISH=m264A.mFISH[rownames(m264A.mFISH)!=row,]

m264A.meta=read.table("/Volumes/multifish/CEA_analysis/CEA_455264_A/segmentation/roi_intact_withCTB_zscore_v3.csv",sep=",",as.is=T,row.names=1, header= TRUE)

```

```{r}
m264M.mFISH=read.table("/Volumes/multifish/CEA_analysis/CEA_455264_M/analysis/1_raw_v2/count_roi_v2.csv",sep=",",as.is=T,row.names=1,header= TRUE)

m264M.mFISH=t(m264M.mFISH)

m264M.mFISH=m264M.mFISH[rownames(m264M.mFISH)!=row,]

m264M.meta=read.table("/Volumes/multifish/CEA_analysis/CEA_455264_M/segmentation/roi_intact_withCTB_zscore_v3.csv",sep=",",as.is=T,row.names=1, header= TRUE)

```
```{r}
m264P.mFISH=read.table("/Volumes/multifish/CEA_analysis/CEA_455264_P/analysis/1_raw_v2/count_roi_v2.csv",sep=",",as.is=T,row.names=1,header= TRUE)

m264P.mFISH=t(m264P.mFISH)

m264P.mFISH=m264P.mFISH[rownames(m264P.mFISH)!=row,]

m264P.meta=read.table("/Volumes/multifish/CEA_analysis/CEA_455264_P/segmentation/roi_intact_withCTB_zscore_v3.csv",sep=",",as.is=T,row.names=1, header= TRUE)

```
```{r}
m265A.mFISH=read.table("/Volumes/multifish/CEA_analysis/CEA_455265_A//analysis/1_raw_v2/count_roi_v2.csv",sep=",",as.is=T,row.names=1,header= TRUE)

m265A.mFISH=t(m265A.mFISH)

m265A.mFISH=m265A.mFISH[rownames(m265A.mFISH)!=row,]

m265A.meta=read.table("/Volumes/multifish/CEA_analysis/CEA_455265_A/segmentation/roi_intact_withCTB_zscore_v3.csv",sep=",",as.is=T,row.names=1, header= TRUE)

```

```{r}
m265M.mFISH=read.table("/Volumes/multifish/CEA_analysis/CEA_455265_M//analysis/1_raw_v2/count_roi_v2.csv",sep=",",as.is=T,row.names=1,header= TRUE)

m265M.mFISH=t(m265M.mFISH)

m265M.mFISH=m265M.mFISH[rownames(m265M.mFISH)!=row,]

m265M.meta=read.table("/Volumes/multifish/CEA_analysis/CEA_455265_M/segmentation/roi_intact_withCTB_zscore_v3.csv",sep=",",as.is=T,row.names=1, header= TRUE)

```

```{r}
m265P.mFISH=read.table("/Volumes/multifish/CEA_analysis/CEA_455265_P//analysis/1_raw_v2/count_roi_v2.csv",sep=",",as.is=T,row.names=1,header= TRUE)

m265P.mFISH=t(m265P.mFISH)

m265P.mFISH=m265P.mFISH[rownames(m265P.mFISH)!=row,]

m265P.meta=read.table("/Volumes/multifish/CEA_analysis/CEA_455265_P/segmentation/roi_intact_withCTB_zscore_v3.csv",sep=",",as.is=T,row.names=1, header= TRUE)

```
### Create Seurat objects
```{r}
m265A <- CreateSeuratObject(m265A.mFISH, meta.data=m265A.meta, project = "m265A")
m265M <- CreateSeuratObject(m265M.mFISH, meta.data=m265M.meta, project = "m265M")
m265P <- CreateSeuratObject(m265P.mFISH, meta.data=m265P.meta, project = "m265P")

m264A <- CreateSeuratObject(m264A.mFISH, meta.data=m264A.meta, project = "m264A")
m264M <- CreateSeuratObject(m264M.mFISH, meta.data=m264M.meta, project = "m264M")
m264P <- CreateSeuratObject(m264P.mFISH, meta.data=m264P.meta, project = "m264P")


CEA_mFISH <- merge(x=m264A, y=c(m264M, m264P, m265A, m265M, m265P), 
                   add.cell.ids=c("m264A", "m264M", "m264P", "m265A", "m265M", "m265P"), 
                   project="mFISH")
```

```{r}
CEA_mFISH <- AddMetaData(
    object = CEA_mFISH,
    metadata =Idents(CEA_mFISH),
    col.name = 'samples')
```

```{r}
save(CEA_mFISH,file="/Users/wangy6/Desktop/DATA/MultiFISH/CTB experiments/CEA_mFISH/R_Seurat_analysis/V3_Nov27/CEA_mFISH_2021Nov27.Robj")
```


```{r}
load("/Users/wangy6/Desktop/DATA/MultiFISH/CTB experiments/CEA_mFISH/R_Seurat_analysis/V3_Nov27/CEA_mFISH_2021Nov27.Robj")
```

###Gene list (ordered): 

```{r}
markers=rownames(CEA_mFISH)
```

###z-score transformation of mFISH data 
```{r}
CEA_mFISH<- ScaleData(CEA_mFISH)
```

### Run PCA and Non-linear dimensional reduction (tSNE) 
```{r, fig.height=5, fig.width=7, message=FALSE, warnings=FALSE}

CEA_mFISH <- RunPCA(CEA_mFISH, npcs = 29,verbose = TRUE,features=markers,approx=FALSE)

#CEA_mFISH <- RunTSNE(CEA_mFISH, seed.use=1, dims=1:29, perplexity=50,check_duplicates = FALSE)

#CEA_mFISH <- RunTSNE(CEA_mFISH, seed.use=1, features =markers, perplexity=50,check_duplicates = FALSE)

CEA_mFISH <- RunUMAP(CEA_mFISH, dims=1:29,n.neighbors = 40L,min.dist = 0.2,)
```


```{r,fig.height=2, fig.width=2.5}
DimPlot(CEA_mFISH, reduction = "umap",pt.size=0.01) 
```

#Use low resolution, this is only to subdivide them into Excitatory and inhibitory populations

```{r}
CEA_mFISH <- FindNeighbors(CEA_mFISH, reduction = "pca",dims = 1:29,k.param = 25)
#CEA_mFISH <- FindNeighbors(CEA_mFISH, features=markers,k.param = 25)
CEA_mFISH  <- FindClusters(CEA_mFISH , algorithm=2,resolution = .1,)
```

```{r}
CEA_mFISH=ReorderIdent(CEA_mFISH,var='area',reorder.numeric=TRUE)
```


```{r,fig.height=2, fig.width=2.5}
DimPlot(CEA_mFISH, reduction = "umap",pt.size=0.01) 
```
#Because the tsne and umap plot look very similar to V1 (previous version), so used the same parameter for clustering 

##k.parameter=25 and resolution=0.1 for initial clustering
```{r,fig.height=2, fig.width=6}
FeaturePlot(CEA_mFISH, reduction='umap',features=c('Gad1','area'), min.cutoff='q1',max.cutoff='q99',pt.size = 0.01,ncol=3)
```


```{r}
library(Seurat)
library(patchwork)
library(ggplot2)

## remove the x-axis text and tick
## plot.margin to adjust the white space between each plot.
## ... pass any arguments to VlnPlot in Seurat
modify_vlnplot<- function(obj, 
                          feature, 
                          pt.size = 0, 
                          plot.margin = unit(c(-0.75, 0, -0.75, 0), "cm"),
                          ...) {
  p<- VlnPlot(obj, features = feature, pt.size = pt.size, ... )  + 
    xlab("") + ylab(feature) + ggtitle("") + 
    theme(legend.position = "none", 
          axis.text.x = element_blank(), 
          axis.ticks.x = element_blank(), 
          axis.title.y = element_text(size = rel(1), angle = 0), 
          axis.text.y = element_text(size = rel(1)), 
          plot.margin = plot.margin ) 
  return(p)
}

## extract the max value of the y axis
extract_max<- function(p){
  ymax<- max(ggplot_build(p)$layout$panel_scales_y[[1]]$range$range)
  return(ceiling(ymax))
}


## main function
StackedVlnPlot<- function(obj, features,
                          pt.size = 0, 
                          plot.margin = unit(c(-0.75, 0, -0.75, 0), "cm"),
                          ...) {
  
  plot_list<- purrr::map(features, function(x) modify_vlnplot(obj = obj,feature = x, ...))
  
  # Add back x-axis title to bottom plot. patchwork is going to support this?
  plot_list[[length(plot_list)]]<- plot_list[[length(plot_list)]] +
    theme(axis.text.x=element_text(), axis.ticks.x = element_line())
  
  # change the y-axis tick to only max value 
 # ymaxs<- purrr::map_dbl(plot_list, extract_max)
 # plot_list<- purrr::map2(plot_list, ymaxs, function(x,y) x + 
 #                           scale_y_continuous(breaks = c(y)) + 
  #                          expand_limits(y = y))

  p<- patchwork::wrap_plots(plotlist = plot_list, ncol = 1)
  return(p)
}
```


```{r,fig.width=5,fig.height=2}
ggsave("/Volumes/multifish/CEA_analysis/figures/mFISH/vlnplot_mFISH_CEA_with_nonneuron_V4.pdf", 
StackedVlnPlot(CEA_mFISH,features=c('nFeature_RNA','nCount_RNA','Gad1','area'),
pt.size=0), width = 6, height = 4,dpi = 50)
```

```{r,fig.width=5,fig.height=2}
ggsave("/Volumes/multifish/CEA_analysis/figures/mFISH/tsne_mFISH_CEA_with_nonneuron_V4.pdf", 
DimPlot(CEA_mFISH, reduction = "umap",pt.size=1,label=TRUE,raster=TRUE) , width = 5, height = 4,dpi = 50)
```


```{r}
StackedVlnPlot(CEA_mFISH,features=c('nFeature_RNA','nCount_RNA','Gad1','area'),
pt.size=0)
```
```{r}
save(CEA_mFISH,file="/Users/wangy6/Desktop/DATA/MultiFISH/CTB experiments/CEA_mFISH/R_Seurat_analysis/V5_Oct2022/CEA_mFISH_2022Oct.Robj")
```


