---
title: "R Notebook"
output: html_notebook
---

###Call for packages
```{r}
library(Seurat)
library(ggplot2)
library(tidyverse)
library(cowplot)
library(scclusteval)
packageVersion("Seurat")
```


```{r}
load("/xxx.Robj")
```

#Clustering of Neurons!!!!
###Finalize the parameters for clustering (k=45, resolution=1, use PCA to cluster)

```{r}
CEA_mFISH_neuron=subset(CEA_mFISH, ident=c(1),invert = TRUE)
```

###z-score transformation of mFISH data 
```{r}
CEA_mFISH_neuron<- ScaleData(CEA_mFISH_neuron)
```

### Run PCA and Non-linear dimensional reduction (tSNE) 
```{r, fig.height=5, fig.width=7, message=FALSE, warnings=FALSE}

CEA_mFISH_neuron <- RunPCA(CEA_mFISH_neuron, npcs = 29,verbose = TRUE,features=rownames(CEA_mFISH_neuron),approx=FALSE)
ElbowPlot(CEA_mFISH_neuron,ndims=29)
#CEA_mFISH_neuron <- RunTSNE(CEA_mFISH_neuron, dims=1:29, perplexity=50,check_duplicates = FALSE)
CEA_mFISH_neuron <- RunUMAP(CEA_mFISH_neuron, dims=1:29,verbose=FALSE,min.dist=0.1,n.neighbors = 20L)
```

```{r}
CEA_mFISH_neuron <- FindNeighbors(CEA_mFISH_neuron,reduction='pca',dims=1:29,k.param = 45)
CEA_mFISH_neuron  <- FindClusters(CEA_mFISH_neuron , algorithm=2,resolution =1,)
```
```{r}
DimPlot(CEA_mFISH_neuron, reduction = "umap",pt.size=0.01,label=TRUE) 
```
```{r,fig.width=12,fig.height=2}
DimPlot(CEA_mFISH_neuron_new, reduction = "umap",split.by='samples',pt.size=0.1,label=TRUE) 
```


###For final neuron clustering, use pca as features, k. param=45, resolution=1 
```{r}
CEA_mFISH_neuron <- FindNeighbors(CEA_mFISH_neuron,features=markers,k.param =45)
CEA_mFISH_neuron  <- FindClusters(CEA_mFISH_neuron , algorithm=2,resolution =1,)

CEA_mFISH_neuron$orig.ident=Idents(CEA_mFISH_neuron)
CEA_mFISH_neuron_sub=RandomSubsetData(CEA_mFISH_neuron, rate=0.8)
CEA_mFISH_neuron_sub<- CEA_mFISH_neuron_sub%>%ScaleData()%>% FindNeighbors(features=markers,k.param =40) %>% FindClusters(algorithm=2,resolution = 1)
PairWiseJaccardSetsHeatmap(CEA_mFISH_neuron_sub$orig.ident,CEA_mFISH_neuron_sub@active.ident, best_match = TRUE)
```
#  Determine the stability of clusters
```{r}

CEA_mFISH_neuron <- FindNeighbors(CEA_mFISH_neuron,feaetures=markers,k.param =45)
CEA_mFISH_neuron  <- FindClusters(CEA_mFISH_neuron , algorithm=2,resolution =1,)

CEA_mFISH_neuron$orig.ident=Idents(CEA_mFISH_neuron)
a=list()
b=list()

x=1
repeat {
CEA_mFISH_neuron_sub=RandomSubsetData(CEA_mFISH_neuron, rate=0.9)
  CEA_mFISH_neuron_sub<- CEA_mFISH_neuron_sub%>%ScaleData()%>% FindNeighbors(features=markers,k.param =40) %>% FindClusters(algorithm=2,resolution =1)

a=append(a,list(CEA_mFISH_neuron_sub$orig.ident))
b=append(b,list(CEA_mFISH_neuron_sub@active.ident))

rm(CEA_mFISH_neuron_sub)
x=x+1
if (x == 51){
break
}
}

JaccardRainCloudPlot(a,b)+ geom_hline(yintercept = c(0.5),linetype = 2) +ylim(0,1)
```

# Merge confusing clusters, merge 19 to 5, it is the BLA cluster. 
```{r,fig.height=2, fig.width=2.5}
CEA_mFISH_neuron_new=RenameIdents(CEA_mFISH_neuron, '19' = '5')
CEA_mFISH_neuron_new <- ReorderIdent(CEA_mFISH_neuron_new, var='nCount_RNA', reverse=TRUE, reorder.numeric = TRUE)
DimPlot(CEA_mFISH_neuron_new, reduction = "umap",pt.size=0.01,label=TRUE) 
```
#Refine clusters 3, 7 and 15 (They share similar gene expression)
```{r}
C=subset(CEA_mFISH_neuron_new, ident=c('3','7','15'))
C <- C %>% FindNeighbors() %>%FindClusters(algorithm=2,resolution =0.1)
CEA_mFISH_neuron_new <-SetIdent(CEA_mFISH_neuron_new, cells=WhichCells(C,ident='0'), value='15')
CEA_mFISH_neuron_new <-SetIdent(CEA_mFISH_neuron_new, cells=WhichCells(C,ident='1'), value='3')
CEA_mFISH_neuron_new <-SetIdent(CEA_mFISH_neuron_new, cells=WhichCells(C,ident='2'), value='7')
CEA_mFISH_neuron_new=RenameIdents(CEA_mFISH_neuron_new, '24' = '22')
CEA_mFISH_neuron_new=RenameIdents(CEA_mFISH_neuron_new, '23' = '22')
CEA_mFISH_neuron_new <- ReorderIdent(CEA_mFISH_neuron_new, var='nCount_RNA', reverse=TRUE, reorder.numeric = TRUE)
DimPlot(CEA_mFISH_neuron_new, reduction = "umap",pt.size=0.01,label=TRUE)
```

# Save Seurat Object
```{r,fig.height=2, fig.width=2.5}
save(CEA_mFISH_neuron_new,file="/XXXX.Robj")
```
